\documentclass[11pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage[LY1,T1]{fontenc}
%\usepackage{frutigernext}
%\usepackage[lf,minionint]{MinionPro}
\usepackage{tikz}
\usetikzlibrary{shapes,positioning,arrows,fit,calc,graphs,graphs.standard}
\usepackage[nosf]{kpfonts}
\usepackage[t1]{sourcesanspro}
\usepackage{multicol}
\usepackage{wrapfig}
\usepackage[top=4mm,bottom=4mm,left=4mm,right=4mm]{geometry}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{microtype}
\usepackage{pdfpages}
\usepackage[shortlabels]{enumitem}
\usepackage{flushend}
\usepackage[abbreviations]{foreign}
\usepackage{tcolorbox}
\usepackage{amsthm}
\usepackage{caption}


\raggedend 

\newif\iflong
\longtrue % \longfalse for short version and \longtrue for long version
\newcommand{\inLongVersion}[1]{\iflong #1\fi}


\setlist{nosep}
\setlist[itemize]{leftmargin=*}
\setlist[enumerate]{leftmargin=*}

\newcommand{\score}{\text{score}}
\newcommand{\encoder}{\text{encoder}}
\newcommand{\decoder}{\text{decoder}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Dist}{\mathcal{D}}
\newcommand{\normal}{\mathcal{N}}
\newcommand{\prob}{\mathbb{P}}
\newcommand{\HEADER}[1]{\begin{tcolorbox}
    \centering
    #1
\end{tcolorbox}}

\DeclareMathOperator{\cov}{\textbf{Cov}}
\DeclareMathOperator{\var}{\textbf{Var}}
\DeclareMathOperator{\argmin}{\textbf{argmin}}
\DeclareMathOperator{\argmax}{\textbf{argmax}}
\DeclareMathOperator{\sgn}{\textbf{sgn}}
\DeclareMathOperator{\dir}{\textbf{Dir}}
\DeclareMathOperator{\cat}{\textbf{Cat}}
\DeclareMathOperator{\vol}{\textbf{vol}}
\DeclareMathOperator{\nnz}{\textbf{nnz}}
\DeclareMathOperator{\Tr}{\textbf{Tr}}
\DeclareMathOperator{\im}{\textbf{im}}
\DeclareMathOperator{\val}{\textbf{val}}
\DeclareMathOperator{\diag}{\textbf{diag}}







\let\bar\overline

\include{./def}

\begin{document}
%\footnotesize
\small
\begin{multicols*}{2}

% Part 1: Convex Optimization

\HEADER{Convex Optimization}

\emph{The first section introduces the notion of convexity. The second section discusses the Lagrangian method, often used to solve the convex optimization exactly. The third section discusses the convergence of numerical methods to solve the convex optimization.}

\input{sections/convexity/convex_chracteristic}

\input{sections/convexity/lagrange}

\input{sections/convexity/gradient_descent}


% Part 2: spectral graph theory


\HEADER{Spectral Graph Theory}

\emph{The first two sections discuss graph Laplacian in the spectral domain, by bounding its eigenvalues and introducing its importance (Cheeger's inequality). The random walk section provides a use case of graph spectral in the analysis of convergence, and introduces the importance of Laplacian linear equations. The next two sections show how to solve Laplacian linear equations exactly by applying pseudo inverse, as the Laplacian is non-invertible. The last two sections show how to approximate a graph Laplacian and solve the Laplacian linear equation approximately but more efficiently.}

\input{sections/spectral/eigen_bound}

\input{sections/spectral/conductance}

\input{sections/spectral/random_walk}

\input{sections/spectral/pseudo_inverse}

\input{sections/spectral/gaussian_elimination}

\input{sections/spectral/random_matrix_concentration}

\input{sections/spectral/approximate_linear}

% Part 3: Combinatorial Graph Algorithms

\HEADER{Combinatorial Graph Algorithms}

\emph{The first section introduces the max flow problem and its duality with min cut, and the Ford-Fulkerson's algorithm which may not terminate in a general graph. The second section introduces the Dinic's algorithm, which can solve the max flow in a general graph. The third section introduces the link-cut tree, and how this can be adopted to speed up the Dinic's algorithm. The fourth section introduces how solving max flow can potentially help to solve other problems. The fifth section introduces interior point method, based on solving max flows. The last second briefly discusses how the distance oracle can be used to approximately solve the shortest distance queries.}

\input{sections/combinatorial/maximum_flow}

\input{sections/combinatorial/dinic}

\input{sections/combinatorial/link-cut-tree}

\input{sections/combinatorial/cut-matching}

\input{sections/combinatorial/interior_point}

\input{sections/combinatorial/distance_oracles}

\end{multicols*}
\end{document}
